---
title: "Table S7.xlsx"
output: html_document
---

Δ (delta) connectivity measures between Smed ELAC2 KD and controls per edge and time point.


**Mention in thesis (for traceability):**

> To identify Smed ELAC2 KD-specific effects, a Δ (delta) connectivity measure was used between Smed ELAC2 KD and controls per edge and time point. For each edge, Δ can be positive or negative. A positive Δ means the connection was stronger in Smed ELAC2 KD than expected from controls, while a negative Δ means it was weaker. Uncertainty was assessed by repeated resampling of cells, which provided confidence intervals for Δ (Section 3.16; Supplementary Table S7). For the family-level visualization, edges with very small absolute changes were ignored, specifically, changes with |Δ| < 0.003 were treated as negligible for the summary plot (Figure 32).


- <a href="tables/Table%20S7.xlsx" download>Download original XLSX</a>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
tab_dir <- normalizePath(file.path('..','tables'), winslash='/', mustWork=TRUE)
fname <- "Table S7.xlsx"
path_abs <- file.path(tab_dir, fname)
```

```{r}
sheets <- tryCatch(readxl::excel_sheets(path_abs), error = function(e) character())
if (length(sheets) == 0) {
  htmltools::tags$em('(No readable sheets.)')
} else {
  blocks <- lapply(sheets, function(sh) {
    dat <- tryCatch(readxl::read_excel(path_abs, sheet = sh), error = function(e) NULL)
    if (is.null(dat)) {
      return(htmltools::tagList(
        htmltools::tags$h2(paste0('Sheet: ', sh)),
        htmltools::tags$em('(Could not read this sheet.)')
      ))
    }
    dt <- DT::datatable(as.data.frame(dat), rownames=FALSE, extensions=c('Buttons','Scroller'),
      options=list(pageLength=25, scrollX=TRUE, scrollY=520, scroller=TRUE, dom='Bfrtip',
        buttons=c('copy','csv','excel'), searchHighlight=TRUE))
    htmltools::tagList(
      htmltools::tags$h2(paste0('Sheet: ', sh)),
      dt
    )
  })
  htmltools::tagList(blocks)
}
```
